Ethnicity sensitive author disambiguation using semi-supervised learning

### 2015-08-26 paper/paper.tex
save

The simplest and most common strategy for blocking, referred to hereon as \emph{SFI},
groups signatures together if they share the same surname(s) and the same first
given name initial (\eg, \emph{SFI}("Doe, John") $==$ "Doe, J").
Despite satisfactory performance, there are several cases where this simple strategy fails to cluster related pairs of signatures together, including:

>>>>

The simplest and most common strategy for blocking, referred to hereon in as \emph{SFI},
groups signatures together if they share the same surname(s) and the same first
given name initial (\eg, \emph{SFI}("Doe, John") $==$ "Doe, J").
Despite satisfactory performance, there are several cases where this simple strategy fails to cluster related pairs of signatures together, including:
